My title

### 2024-11-01 paper/paper.qmd
1. missing citations updated, some format problem fixed. 2. Unneeded files deleted 3. llm usage updated

## Analysis Data
This analysis is focused on Donald Trump, so we only collected observations where the candidate_name is Trump. At the same time, we prioritize the quality of the polls. In a political approval rate prediction model, which is often influenced by numerous complex factors, we encounter data that is typically complex and noisy. Low-quality poll results can introduce significant bias into our prediction model, further impacting the accuracy of inferences. Therefore, only polls with a numeric_grade above 2.7 were selected. Additionally, Trump's main opponent, Kamala Harris, only entered the race after Biden’s withdrawal, a major political event that could have significant effects on the support rates for both sides. As such, we focused solely on polls conducted after Biden’s withdrawal to enhance the model’s prediction accuracy for the final outcome.

@@

The following figures, @fig-pollstermetho, @fig-state and @fig-overtime, display various aspects of data related to Trump's support rate, helping us understand how support rates vary with different factors. In @fig-pollstermetho and @fig-state, we have marked the occurrence count of each pollster or state on the x-axis, helping us identify potential sources of bias in the data. Low-frequency items (such as data points from certain pollsters or states) may reduce the representativeness of the model—low-frequency observations imply insufficient data for specific pollsters or states, which may not accurately reflect voter support rates in these areas. This incomplete data could lead to unreliable predictions for these pollsters or states, increasing prediction errors. Additionally, low-frequency data is more susceptible to extreme values. With fewer observations, certain outlier data points (e.g., a particularly high or low support rate in a single poll) can appear disproportionately significant, affecting the overall prediction. When fitting the model to low-frequency data, it may be more influenced by the "noise" in these data points, potentially introducing bias into the overall results. Systematic biases in low-frequency observations could spread throughout the model, impacting the overall accuracy of the predictions.

@@

The goal of our modelling strategy is to build a time series model to predict the percentage of support for Trump over time. This model incorporates multiple variables, including the polling methodology (methodology), the number of days since Biden's withdrawal from the race on 21 July 2024 (days_since_Biden_Withdrawal), whether the poll is at the national level (is_national), as well as random effects for each state (state) and each pollster (pollster).  These variables are chosen to capture the effects of time, polling characteristics, and geographic location on support rates, allowing us to obtain dynamic estimates of support for Trump and to predict the winner of 2024 U.S. presidential election.

@@

For the variable `days_since_Biden_Withdrawal`, we hypothesize that, over time, Trump’s approval ratings may fluctuate due to shifts in the election landscape, policy discussions, and changes in voter sentiment. This hypothesis is based on the dynamic nature of polling data: as elections near their end, poll results typically converge, reflecting more accurate forecasts for election day (see @blumenthal2010polls). We anticipate that the `days_since_Biden_Withdrawal` variable may exhibit a positive or negative trend, depending on the political climate and voter responses to Trump in particular periods.

Through the `is_national` variable, we distinguish between national and state-level polls, this variable enables the model to capture support rate differences arising from geographic and demographic differences. We expect that national polls, which typically have larger and more representative samples, are better suited to capturing overall trends, while state-level polls may reflect finer, localized biases and specific regional issues because national polls often encompass a broader and more balanced voter base, they provide a more stable forecast of overall voter trends. In contrast, due to geographic and demographic variations, state-level polls often exhibit greater fluctuations in error than national polls. These fluctuations stem from regional issues and diverse demographic characteristics, which may not align fully with national trends (see @kennedy2018disentangling).

@@

# Results
## Model Output
Our results are summarized in a table which is available [here](https://8360846bf92342d59862bf4ec3515643.app.posit.cloud/file_show?path=%2Fcloud%2Fproject%2Fpaper%2Fmodel_summary_table.html). This summary reveals the effects of different polling methods and organizations on our estimates. For instance, there is a small difference in estimates between data collected via online panels and phone surveys. The model adjusts for these differences by using a hierarchical structure, which accounts for inconsistencies caused by methodological and organizational biases. Specifically, variance parameters for different methods indicate the different impacts these methods have on sampling coverage and voter behavior, helping the model balance these differences.

@@

## Winner Prediction
Based on the support rate predictions for Trump at both the national and state levels displayed in the charts in the results section, it appears challenging for Trump to emerge victorious in the upcoming U.S. presidential election on November 5, 2024, against his primary opponent, Harris. The first chart shows the national support rate prediction for Trump, centering around 45% to 50%. Historically, any candidate needs to reach or exceed the 50% threshold to secure a decisive victory. The current predictions reveal some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with a possibility of winning.

The second chart illustrates the support rates at the state level, revealing significant differences between red and blue states. For instance, Trump’s predicted support rate is higher in traditionally conservative states such as Texas, while in strong Democratic states like California, his support rate is lower. In swing states like Pennsylvania and Michigan, the support rate hovers around 50%, aligning with historical trends where these states tend to have close contests.

To draw final conclusions from these predictions, it is essential to consider historical polling data and past election results. In previous U.S. presidential elections, shifts in sentiment in swing states have played a crucial role in determining the outcome. For example, the 2016 election highlighted the importance of swing states like Pennsylvania, Michigan, and Wisconsin, where polls underestimated Trump’s support. A study by the Pew Research Center noted that last-minute sentiment shifts and polling errors led to an unexpected advantage for Trump (source: Pew Research Center). Studies by *The Economist* and *FiveThirtyEight* emphasize the critical impact of swing states on election outcomes, also noting that national polls do not always reflect the dynamics of the Electoral College (source: The Economist). The Electoral College system can result in a candidate winning the popular vote but losing the election, or vice versa. This system has affected U.S. elections multiple times, demonstrating the importance of state-level results relative to national polling trends (source: National Archives).

Given the current support rate predictions from our model and the historical performance of swing states, it is projected that Trump may not secure a clear victory. Furthermore, the volatility in swing states suggests that if these states lean Democratic as they did in 2020, Harris would likely win. However, the final outcome will depend on voter turnout, the last stages of the campaign, and any major events leading up to Election Day.

## Weaknesses and next steps
In discussing the limitations of polls and our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior. Each step, from data collection to model construction, involves certain assumptions and potential biases. Below is a detailed discussion of these aspects:

@@

### The Influence of Reality
#### Bias and Transparency
The influence of polling agencies’ biases and methodological transparency on election predictions has long been a research focus. Every polling agency's choices—whether intentional or unintentional—can introduce biases into results. In highly polarized political environments, factors like question wording, sampling techniques, and demographic weighting can amplify potential biases. For example, research from the [Pew Research](https://www.pewresearch.org/short-reads/2024/08/28/key-things-to-know-about-us-election-polling-in-2024/) Center and [Stanford University](https://news.stanford.edu/stories/2020/10/9-things-know-election-polling-data) shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump (see @pew2024electionpolling and @stanford2020electionpolling).

Another complex issue is "partisan nonresponse bias," where certain political groups are less likely to participate in polls. This trend has become more prominent in recent years, notably affecting conservative respondents. Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely (see @pew2024electionpolling).

Additionally, there is a feedback loop between published poll results and voter behavior: trends shown in polls can influence undecided voters or shift the enthusiasm levels of a candidate's supporters. The presence of "shy" or undecided voters further complicates the challenge of accurate polling. Despite methodological advancements, polling remains prone to errors that are often underestimated compared to the actual unpredictability of elections (source3).

@@

According to a [Pew Research Center report](https://www.pewresearch.org/methods/2021/04/08/confronting-2016-and-2020-polling-limitations/), polling biases often stem from financial constraints and methodological choices, such as the use of cost-effective online panels, which may not effectively capture perspectives from older, rural, or technologically less-adept groups. These groups often require different recruitment strategies and data collection methods, increasing polling costs (see @pew2021pollinglimitations). Another [Pew report](https://www.pewresearch.org/politics/2024/09/09/issues-and-the-2024-election/) highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques (see @pew2024issues).

@@

#### The Randomness of the Real World
Voter preferences can shift rapidly due to events like debates, economic changes, or international incidents, challenging election predictions. Regular polling may fail to capture these shifts if not updated frequently, leading to outdated and potentially misleading forecasts. The [Harvard Data Science Review](https://hdsr.mitpress.mit.edu/pub/nw1dzd02/release/2) highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions (@gelman2020regression).

>>>>

## Analysis Data
This analysis is focused on Donald Trump, so we only collected observations where the `candidate_name` is Trump. At the same time, we prioritize the quality of the polls. In a political approval rate prediction model, which is often influenced by numerous complex factors, we encounter data that is typically complex and noisy. Low-quality poll results can introduce significant bias into our prediction model, further impacting the accuracy of inferences. Therefore, only polls with a `numeric_grade` above 2.7 were selected. Additionally, Trump's main opponent, Kamala Harris, only entered the race after Biden’s withdrawal, a major political event that could have significant effects on the support rates for both sides. As such, we focused solely on polls conducted after Biden’s withdrawal to enhance the model’s prediction accuracy for the final outcome.

@@

The following figures, @fig-pct1 and @fig-pct2, display various aspects of data related to Trump's support rate, helping us understand how support rates vary with different factors. In @fig-pct1, we have marked the occurrence count of each pollster or state on the x-axis, helping us identify potential sources of bias in the data. Low-frequency items (such as data points from certain pollsters or states) may reduce the representativeness of the model—low-frequency observations imply insufficient data for specific pollsters or states, which may not accurately reflect voter support rates in these areas. This incomplete data could lead to unreliable predictions for these pollsters or states, increasing prediction errors. Additionally, low-frequency data is more susceptible to extreme values. With fewer observations, certain outlier data points (e.g., a particularly high or low support rate in a single poll) can appear disproportionately significant, affecting the overall prediction. When fitting the model to low-frequency data, it may be more influenced by the "noise" in these data points, potentially introducing bias into the overall results. Systematic biases in low-frequency observations could spread throughout the model, impacting the overall accuracy of the predictions.

@@

The goal of our modelling strategy is to build a time series model to predict the percentage of support for Trump over time. This model incorporates multiple variables, including the polling methodology, the number of days since Biden's withdrawal from the race on 21 July 2024, whether the poll is at the national level, as well as random effects for each state and each pollster.  These variables are chosen to capture the effects of time, polling characteristics, and geographic location on support rates, allowing us to obtain dynamic estimates of support for Trump and to predict the winner of 2024 U.S. presidential election.

@@

For the variable `days_since_Biden_Withdrawal`, we hypothesize that, over time, Trump’s approval ratings may fluctuate due to shifts in the election landscape, policy discussions, and changes in voter sentiment. This hypothesis is based on the dynamic nature of polling data: as elections near their end, poll results typically converge, reflecting more accurate forecasts for election day [see @blumenthal2010polls]. We anticipate that the `days_since_Biden_Withdrawal` variable may exhibit a positive or negative trend, depending on the political climate and voter responses to Trump in particular periods.

Through the `is_national` variable, we distinguish between national and state-level polls, this variable enables the model to capture support rate differences arising from geographic and demographic differences. We expect that national polls, which typically have larger and more representative samples, are better suited to capturing overall trends, while state-level polls may reflect finer, localized biases and specific regional issues because national polls often encompass a broader and more balanced voter base, they provide a more stable forecast of overall voter trends. In contrast, due to geographic and demographic variations, state-level polls often exhibit greater fluctuations in error than national polls. These fluctuations stem from regional issues and diverse demographic characteristics, which may not align fully with national trends [see @kennedy2018disentangling].

@@

# Results {#sec-results}
## Model Output
Our results are summarized in a table which is available [here](https://8360846bf92342d59862bf4ec3515643.app.posit.cloud/file_show?path=%2Fcloud%2Fproject%2Fpaper%2Fmodel_summary_table.html). This summary reveals the effects of different polling methods and organizations on our estimates. For instance, there is a small difference in estimates between data collected via online panels and phone surveys. The model adjusts for these differences by using a hierarchical structure, which accounts for inconsistencies caused by methodological and organizational biases. Specifically, variance parameters for different methods indicate the different impacts these methods have on sampling coverage and voter behavior, helping the model balance these differences.

@@

## Winner Prediction {#sec-pred}
Based on the support rate predictions for Trump at both the national and state levels displayed in @fig-results in @sec-results, it appears challenging for Trump to emerge victorious in the upcoming U.S. presidential election on November 5, 2024, against his primary opponent, Harris. The first chart shows the national support rate prediction for Trump, centering around 45% to 50%. Historically, any candidate needs to reach or exceed the 50% threshold to secure a decisive victory. The current predictions reveal some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with some possibility of winning.

The @fig-results also illustrates the support rates at the state level, revealing significant differences between red and blue states. For instance, Trump’s predicted support rate is higher in traditionally conservative states such as Texas, while in strong Democratic states like California, his support rate is lower. In swing states like Pennsylvania and Michigan, the support rate hovers around 50%, aligning with historical trends where these states tend to have close contests.

To draw final conclusions from these predictions, it is essential to consider historical polling data and past election results. In previous U.S. presidential elections, shifts in sentiment in swing states have played a crucial role in determining the outcome. For example, the 2016 election highlighted the importance of swing states like Pennsylvania, Michigan, and Wisconsin, where polls underestimated Trump’s support. A study by the Pew Research Center noted that last-minute sentiment shifts and polling errors led to an unexpected advantage for Trump [@pew2021pollinglimitations]. Studies by *The Economist* emphasize the critical impact of swing states on election outcomes, also noting that national polls do not always reflect the dynamics of the Electoral College [see @economist2020electionforecast]. The Electoral College system can result in a candidate winning the popular vote but losing the election, or vice versa. This system has affected U.S. elections multiple times, demonstrating the importance of state-level results relative to national polling trends.

Given the current support rate predictions from our model and the historical performance of swing states, it is projected that Trump cannot secure a clear victory. Furthermore, the volatility in swing states suggests that if these states lean Democratic as they did in 2020, Harris would likely win. However, the final outcome will depend on voter turnout, the last stages of the campaign, and any major events leading up to Election Day.

## Weaknesses and next steps {#sec-weakness}
In discussing the limitations of polls and our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior. Each step, from data collection to model construction, involves certain assumptions and potential biases. Below is a detailed discussion of these aspects:

@@

### The Influence of Reality
#### Bias and Transparency
The influence of polling agencies’ biases and methodological transparency on election predictions has long been a research focus. Every polling agency's choices—whether intentional or unintentional—can introduce biases into results. In highly polarized political environments, factors like question wording, sampling techniques, and demographic weighting can amplify potential biases. For example, research from the [Pew Research](https://www.pewresearch.org/short-reads/2024/08/28/key-things-to-know-about-us-election-polling-in-2024/) Center and [Stanford University](https://news.stanford.edu/stories/2020/10/9-things-know-election-polling-data) shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump [see @pew2024electionpolling and @stanford2020electionpolling].

Another complex issue is "partisan nonresponse bias," where certain political groups are less likely to participate in polls. This trend has become more prominent in recent years, notably affecting conservative respondents. Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely [see @pew2024electionpolling].

Additionally, there is a feedback loop between published poll results and voter behavior: trends shown in polls can influence undecided voters or shift the enthusiasm levels of a candidate's supporters. The presence of "shy" or undecided voters further complicates the challenge of accurate polling. Despite methodological advancements, polling remains prone to errors that are often underestimated compared to the actual unpredictability of elections.

@@

According to a [Pew Research Center report](https://www.pewresearch.org/methods/2021/04/08/confronting-2016-and-2020-polling-limitations/), polling biases often stem from financial constraints and methodological choices, such as the use of cost-effective online panels, which may not effectively capture perspectives from older, rural, or technologically less-adept groups. These groups often require different recruitment strategies and data collection methods, increasing polling costs [see @pew2021pollinglimitations]. Another [Pew report](https://www.pewresearch.org/politics/2024/09/09/issues-and-the-2024-election/) highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques [see @pew2024issues].

@@

#### The Randomness of the Real World
Voter preferences can shift rapidly due to events like debates, economic changes, or international incidents, challenging election predictions. Regular polling may fail to capture these shifts if not updated frequently, leading to outdated and potentially misleading forecasts. The [Harvard Data Science Review](https://hdsr.mitpress.mit.edu/pub/nw1dzd02/release/2) highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions [@gelman2020regression].
